Speeding up prediction performance of the BDT-based models

### 2017-11-11 acat_paper/paper.tex
fix
refs

\author{
 E. Khairullin$^{1, 3}$
 and
 A. Ustyuzhanin$^{1, 2, 3}$
}
% \address{Production Editor, \jpcs, \iopp, Dirac House, Temple Back, Bristol BS1~6BE, UK}
\address{$^{1}$ Moscow Institute of Physics and Technology}
\address{$^{2}$ National Research University Higher School of Economics, 20 Myasnitskaya st., Moscow 101000, Russia}
\address{$^{3}$ Yandex School of Data Analysis, 11/2, Timura Frunze st., Moscow 119021, Russia}

\ead{mikari@yandex-team.ru, anaderi@yandex-team.ru}

@@

\section{Tensor Similarity}
Let's introduce the metric for the similarity of two tensors. Suppose, we have two tensors: $D^1 = (B^{1}_{1}, ..., B^{1}_{n})$ and $D^2 = (B^{2}_{1}, ..., B^{2}_{n})$. Their sum $D^u = D^1 + D^2$ could be defined as $D^u = (f^{u}_{1}, ..., f^{u}_{f})$, where $f^{u}_{i} = f^{1}_{i} \cup f^{2}_{i}$. Now, let's define similarity as the difference between the sum of their sizes and the size of their union:

@@

\section*{References}
\numrefs{99}
\item Gulin A, Kuralenok I, Pavlov D 2011 {\it Winning The Transfer Learning Track of Yahoo!'s Learning To Rank Challenge with YetiRank.} (Yahoo! Learning to Rank Challenge) p 63--76
\item Likhomanenko T, Ilten P, Khairullin E, Rogozhnikov A, Ustyuzhanin A, Williams M 2015 {\it LHCb Topological Trigger Reoptimization} (Journal of Physics: Conference Series)
\item Dorogush A V, Gulin A, Gusev G, Kazeev N, Ostroumova Prokhorenkova L, Vorobev A {\it Fighting biases with dynamic boosting.} ([arXiv:1706.09516])
\item Gligorov V, Williams M 2013 {\it Efficient, reliable and fast high-level triggering using a bonsai boosted decision tree} (JINST 8 P02013 [arXiv:1210.6861])
\endnumrefs

>>>>

\author{
 E. Khairullin$^{1, 3}$
 and
 A. Ustyuzhanin$^{2, 3}$
}
\address{$^{1}$ Moscow Institute of Physics and Technology, Institutskiy per. 9, Dolgoprudny, Moscow Region, 141700, Russia}
\address{$^{2}$ National Research University Higher School of Economics, 20 Myasnitskaya st., Moscow 101000, Russia}
\address{$^{3}$ Yandex School of Data Analysis, 11/2, Timura Frunze st., Moscow 119021, Russia}

\ead{mikari@yandex-team.ru}

@@

\section{Tensor Similarity}
Let's introduce the metric for the similarity of two tensors. Suppose, we have two tensors: $D^1 = (B^{1}_{1}, ..., B^{1}_{n})$ and $D^2 = (B^{2}_{1}, ..., B^{2}_{n})$. The sum $D^u = D^1 + D^2$ could be defined as $D^u = (f^{u}_{1}, ..., f^{u}_{f})$, where $f^{u}_{i} = f^{1}_{i} \cup f^{2}_{i}$. Now, let's define similarity as the difference between the sum of their sizes and the size of their union:

@@

\section*{References}
\numrefs{99}
\item Gulin A, Kuralenok I, Pavlov D 2011 Winning The Transfer Learning Track of Yahoo!'s Learning To Rank Challenge with YetiRank {\it Yahoo! Learning to Rank Challenge} p 63--76
\item Likhomanenko T, Ilten P, Khairullin E, Rogozhnikov A, Ustyuzhanin A, Williams M 2015 LHCb Topological Trigger Reoptimization (IOP Publishing) {\it Journal of Physics: Conference Series} Vol. 664, No. 8, p. 082025
\item Dorogush A, Gulin A Gusev G Kazeev N Ostroumova L Vorobev A Fighting biases with dynamic boosting arXiv:1706.09516
\item Gligorov V, Williams M 2013 Efficient, reliable and fast high-level triggering using a bonsai boosted decision tree {\it Journal of Instrumentation} 8 P02013
\endnumrefs
